\Title

### 2020-02-18 manuscript/manuscript.tex
Specify number of prisms on synthetic model

The synthetic model is made out of \textbf{number} number of prisms distributed
on a region of \SI{100}{\km}$\times$\SI{100}{\km} between \SI{10}{\km} deep and
the zero height plane.
Density of prisms range from \SI{-900}{\kg\per\cubic\m} and
\SI{500}{\kg\per\cubic\m}.
We created deep big and thin shallow prisms for creating gravity anomalies with
long and short wavelengths, respectively.

>>>>

The synthetic model is made out of 64 prisms distributed on a region of
\SI{100}{\km}$\times$\SI{100}{\km} between \SI{10}{\km} deep and the zero
height plane.
Density of prisms range from \SI{-900}{\kg\per\cubic\m} and
\SI{500}{\kg\per\cubic\m}.
We created deep big and thin shallow prisms for creating gravity anomalies with
long and short wavelengths, respectively.
